Appendix

### 2018-06-11 manuscript/appendix.Rmd
add lakes to gis example

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

iws <- readRDS("../data/iws_extent.rds")
nws <- readRDS("../data/nws_extent.rds")

@@

ggplot() + 
  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
  geom_sf(data = nws) +
  coord_sf(crs = st_crs(nws), datum = NA) + 
  # geom_sf(data = iws) + 
  theme_void()

@@

(m_nes <- tm_shape(us) + tm_polygons() +
          tm_shape(nes_extent) + tm_borders(lwd = 2) +
          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
                                 size = 0.15, legend.show = TRUE, 
                                 title = "Average Link Length")) +
          # tm_credits("National Eutrophication Survey") +
          tm_layout(frame = FALSE,
                    legend.outside = FALSE,
                    legend.stack = "horizontal")
```

@@

ggplot(data = dplyr::filter(nes_nws, 
                     !is.na(avg_link_length))) + 
         geom_point(aes(x = avg_link_length, 
                                        y = p_percent_retention, 
                                        color = grp), 
                                    size = 2) + 
  scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
                     viridis::viridis(1, begin = 0.5))) +
  ylab("P Retention") + xlab("Avg. Link Length") + 
  geom_vline(xintercept = ll_split) + 
  theme(legend.position = "none") 
```

>>>>

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# nws_lakes <- pull_lakes(nws)
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")
# saveRDS(nws_lakes, "../data/nws_lakes.rds")

iws <- readRDS("../data/iws_extent.rds")
nws <- readRDS("../data/nws_extent.rds")
nws_lakes <- readRDS("../data/nws_lakes.rds")

nws_lakes <- nws_lakes[order(st_area(nws_lakes), decreasing = TRUE),]
nws_lakes <- nws_lakes[1:2,]

@@

ggplot() + 
  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
  geom_sf(data = nws) +
  geom_sf(data = nws_lakes[1,], color = "cyan") +
  geom_sf(data = nws_lakes[2,], color = "yellow") +
  coord_sf(crs = st_crs(nws), datum = NA) + 
  # geom_sf(data = iws) + 
  theme_void()

@@

m_nes <- tm_shape(us) + tm_polygons() +
          tm_shape(nes_extent) + tm_borders(lwd = 3) +
          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
                                 size = 0.2, legend.show = TRUE, 
                                 title = "Average Link Length") +
          # tm_credits("National Eutrophication Survey") +
          tm_layout(frame = FALSE,
                    legend.outside = FALSE,
                    legend.stack = "horizontal")

save_tmap(m_nes, "../figures/best_partition_maps-1.png",
          scale = 0.7, width = 3.125)
```

@@

ggplot(data = dplyr::filter(nes_nws, 
                     !is.na(avg_link_length))) + 
         geom_point(aes(x = avg_link_length, 
                                        y = p_percent_retention, 
                                        color = grp), 
                                    size = 1.3) + 
  scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
                     viridis::viridis(1, begin = 0.5))) +
  ylab("P Retention") + xlab("Avg. Link Length") + 
  geom_vline(xintercept = ll_split) + 
  theme(legend.position = "none") 
```
